Notes from the President

### 2022-05-20 pnsac/newsletter/article_EditorsNotes.tex
Updated for final May 2022 issue.

Unfortunately COVID-19 and its restrictions continue to hamper the restoration
of the North Star. So it's a good time to look at what has been accomplished to
date by the restoration team which consists of both Museum staff and volunteers.
This edition will continue the focus on the Merlin engines. As many of you know
many of the volunteers are also members of our organization.

You will find photos of some of those volunteers in the technical article on
engines three and four. You will also find a interview with Garry Dupont who has
had a leading role in the engine shop work.

In the next edition we expect to have more articles about our members
experiences in the restoration project.

In the meantime if you have any comments on this edition or suggestions for
future editions please send them to me.

@@

@@

>>>>

This edition marks a change of leadership of our association. Richard Lodge, our longtime president, retired at the end of 2021. His replacement is Chris McGuffin. Richard's reminiscences of his time as president can be found in the Our Members column.  While Richard's story talks about his past experiences, Chris' Notes from the President sets out his vision for the future of the organization. R\'{e}jean Demers, CASM's Project Manger for the North Star also addresses, in the Conservator's Corner column,  how he envisages the Project restarting this year.  Finally, there is a fascinating article by John Makadi and Christ McGuffin about how they found and acquired an APS 42 radar unit for the aircraft. Good reading.

@@

\noindent As always comments and suggestions for future editions are welcomed.

@@

\vspace{60pt}

### 2022-05-20 pnsac/newsletter/article_Feature1.tex
Updated for final May 2022 issue.

\textit{The article below was written by our members John Makadi and Chris McGuffin. Chris and John played key roles in the acquisition of the APS 42 Radar for the North Star aircraft. In 2019 John was approached by Rejean Demers, CASM's project manager for the North Star restoration to see if he could locate the radar unit which was missing from the aircraft as explained below. John was successful and as a result in 2001  Rej asked Chris if  our association  could arrange for the acquisition of the unit. John and Chris coordinated its acquisition and what follows is a very fascinating story about what may be the only unit of its kind still in existence. The authors have been very modest about their contributions in dealing with a very challenging process made more difficult by the pandemic Covid-19.}

@@

\begin{figure}[H]
   \vspace{2em}
   \centering
   %name of the graphic, without the path AND in EPS format:
   \includegraphics[scale=0.5]{radar_the_unit.png}
   %caption of the figure 
   \caption*{\small \em Radar -- The Unit.}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:img1}
\end{figure}

>>>>

\textit{The article below was written by our members John Makadi and Chris McGuffin. Chris and John played key roles in the acquisition of the APS 42 Radar for the North Star aircraft. In 2019 John was approached by R\'{e}jean Demers, CASM's project manager for the North Star restoration to see if he could locate the radar unit which was missing from the aircraft as explained below. John was successful and as a result in 2001  R\'{e}j asked Chris if  our association  could arrange for the acquisition of the unit. John and Chris coordinated its acquisition and what follows is a very fascinating story about what may be the only unit of its kind still in existence. The authors have been very modest about their contributions in dealing with a very challenging process made more difficult by the pandemic Covid-19.}

@@

\begin{figure}[H]
   \vspace{2em}
   \centering
   %name of the graphic, without the path AND in EPS format:
   \includegraphics[scale=0.45]{radar_the_unit.png}
   %caption of the figure 
   \caption*{\small \em Radar -- The Unit.}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:img1}
\end{figure}

### 2022-05-20 pnsac/newsletter/article_PresReport.tex
Updated for final May 2022 issue.

2022 is going to be a year of renewal in many ways. In January I assumed the presidency of the Association. Our previous president, Rodger Lodge, held the position for nearly 12 years. Roger has been involved with the Association for 20 years and I am thankful that he has agreed to stay on the Board of Directors. The Canada Aviation and Space Museum is actively renovating the conservation workshop. Plans for a return of volunteers to the Museum are being developed and restoration activity should resume in the months ahead. I am grateful for the encouragement of our supporters and the tenacity of our volunteers. We'll be back to the restoration effort soon.

>>>>

2022 is going to be a year of renewal in many ways. In January I assumed the presidency of the Association. Our previous president, Richard Lodge, held the position for nearly 12 years. Richard has been involved with the Association for 20 years and I am thankful that he has agreed to stay on the Board of Directors. The Canada Aviation and Space Museum is actively renovating the conservation workshop. Plans for a return of volunteers to the Museum are being developed and restoration activity should resume in the months ahead. I am grateful for the encouragement of our supporters and the tenacity of our volunteers. We'll be back to the restoration effort soon.
